---
title: "HW1"
author: "Florian John Date:"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

```{r}
library(ggplot2)
```


# Summary 
In this assignment I will explain my previous experiences with R, RStudio, R Markdown, Git, Github, ggplot2 and dplyr. 

After this i will use ggplot to visualize a data-set fetched from the internet. 

# Task 1 

\textit{prior experiences:}

My experiences working with R, RStudio and R Markdown has been limited to projects assignments associated with a few statistical courses relating to inference theory and linear-statistical-models.
I have therefore worked with optimization methods, visualizing data and model selection among other things.

I do not have experience working with Git, Github, ggplot2 and dplyr however i do know that Github is used during collaborative efforts when working on code online.

# Task 2

\textit{Visualisation of data using ggplot:}

We search for a free data-set online and find a data-set containing information about yield, fertilizer-type and water height on Github 
(link: https://raw.githubusercontent.com/Opensourcefordatascience/Data-sets/master/crop_yield.csv).

Using the link to the raw csv file on github we use the read.csv function to obtain a dataset which we name df.

```{r}
set.seed(980205) #my date of birth
link <- "https://raw.githubusercontent.com/Opensourcefordatascience/Data-sets/master/crop_yield.csv"
df <- read.csv(link)
```

We now plot the data using the ggplot function in order to observe the relations between data in the data-set.

```{r}
library(ggplot2)
gg <- ggplot(df,aes(Water,Yield,colour = Fert))
gg <- gg + geom_point()
gg + labs(title = "Yield graph",
          caption = "Figure 1: Graph representing Yield based off water height and fertilizer type")
```

From figure 1 it seems that yield increases when the water level is "High" and the Fertilizer type is "A".

```{r}
sessionInfo()
```

